Scaling rates of true polar wander in convecting planets and moons

### 2016-02-22 tpw_rate.tex
Expand text on infinite time limit of love number

The infinite-time limit of Equation~\eqref{eq:viscoelastic_deformation} allows us to calculate the fluid limit of the Love number $k_f$:
\begin{equation}
k_f = \frac{3 G (C-A)}{\Omega^2 a^5}
\label{eq:fluid_love}
\end{equation}
where $C$ and $A$ are the polar and equatorial moments of inertia, respectively.
The infinite-time limit, however, does not allow for any disequilibrium between $J_{ij}$ and $E_{ij}$.

>>>>

The infinite-time limit of Equation~\eqref{eq:viscoelastic_deformation} for a 
constant rotation vector around the $z$-axis implies
\begin{equation}
\begin{aligned}
J_{zz} = C = &\frac{2}{3} \frac{k_f a^5 \Omega^2}{3 G} \\
J_{xx} = J_{yy} = A = -&\frac{1}{3} \frac{k_f a^5 \Omega^2}{3 G} \\
\end{aligned}
\end{equation}
where $C$ and $A$ are the polar and equatorial moments of inertia, respectively, 
and $k_f$ is the fluid limit of $k$. 
We can solve for $k_f$ in terms of $C-A$:
\begin{equation}
k_f = \frac{3 G (C-A)}{\Omega^2 a^5}
\label{eq:fluid_love}
\end{equation}
This fluid-limit representation of the deformation does not allow for any disequilibrium between $J_{ij}$ and $E_{ij}$,
and so cannot by itself capture the physics of TPW.
